Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex

WE NEED SOMETHING HERE DESCRIBING WHY AN INODE IS A GOOD ABSTRACTION

\begin{figure}[h]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{A ZLog sequencer that uses the CephFS MDS enjoys the load balancing
capabilities of the metadata cluster. The ``Sequencer Baseline'' has no
background sequencers, while the the ``2 Seq'' curves are the throughputs
of 1 sequencer when an additional sequencer is running in the background
generating load.} 
\label{fig:mantle-seq-thruput.png}
\end{figure}

@@

\begin{figure}[h]
\begin{lstlisting}
  -- Metadata server load
  mdsload = MDSs[i]["all"]

@@

Figure~\ref{fig:mantle-seq-thruput.png} gives a macro-level view of the
performance of the Ceph components exposed by Malacology. Each curve shows the
throughput from the perspective of one sequencer ({\it y} axis) over time ({\it
x} axis). The ``Sequencer Baseline'' curve is one sequencer serving 7 clients.
The sequencer operates on an MDS cluster where balancing is turned off and
there are no other workloads running. ``2 Seq; No Load Balancing" adds another
sequencer of equal load running in the background. The performance of the
background sequencer is omitted. ``2 Seq; Mantle Load Balancing" uses a 3 MDS
node cluster to provide the sequencer services, again with a background
sequencer service. Finally, the ``Sequencer Recovery" curve shows the
performance of the sequencer in a multi-MDS cluster with 2 standby MDS nodes.
At 60 seconds, MDS 0 is killed.

@@

\textbf{The Malacology Principle:} Re-uses the Ceph metadata migration, load
balancing, cache coherence, and capabilities subsystems of the MDS. Applying
Mantle's load balancing policy shows 2\(\times\) performance improvent and x\%
of the baseline best-case performance.

@@

- Describe the graph

- We get recovery and load balancing with minimal implementation

\subsection{Load Balancing}

\begin{figure}[h]
\centering
\includegraphics{figures/mantle-cpu-utilization-annotate.png}
\caption{The sequencer using Mantle in Figure~\ref{fig:mantle-seq-thruput.png} migrates to a new MDS immediately because its uses a policy designed for bursty workloads. This is a trace of the same workload running twice: once with a single MDS and once with Mantle.}
\label{fig:mantle-cpu-utilization}
\end{figure}

- Sequencer specific policy

- Describe the graph

- We get tunable policies

\subsection{Recovery}

>>>>

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{A ZLog sequencer that uses the CephFS MDS enjoys the load balancing
capabilities of the metadata cluster. The ``Sequencer Baseline'' has no
background sequencers, while the the ``2 Seq'' curves are the throughputs
of 1 sequencer when an additional sequencer is running in the background
generating load.}\label{fig:mantle-seq-thruput}
\end{figure}

@@

\begin{figure}[]
\begin{lstlisting}
  -- Metadata server load
  mdsload = MDSs[i]["all"]

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-cpu-utilization-annotate.png}
\caption{The sequencer using Mantle in Figure~\ref{fig:mantle-seq-thruput.png}
migrates to a new MDS immediately because its uses a policy designed for bursty
workloads. This is a trace of the same workload running twice: once with a
single MDS and once with Mantle.}
\label{fig:mantle-cpu-utilization}
\end{figure}

Figure~\ref{fig:mantle-seq-thruput} gives a macro-level view of the performance
of the Ceph components exposed by Malacology. Each curve shows the throughput
from the perspective of one sequencer (\(y\) axis) over time (\(x\) axis).  The
``Sequencer Baseline'' curve is one sequencer serving 7 clients.  The sequencer
operates on an MDS cluster where balancing is turned off and there are no other
workloads running. ``No Load Balancing" adds another sequencer of equal load
running in the background. The performance of the background sequencer is
omitted. The last two policies, ``Sequencer Balancing Policy" and
``Conservative Balancing Policy", show the performance of the sequencer (with a
background sequencer running) when using Mantle with a 3 MDS node cluster.
These policies differ by the threshold at which they start balancing:
``Sequencer Balancing Policy" starts balancing immediately and ``Conservative
Balancing Policy" waits for 120 seconds.

Figure~\ref{fig:mantle-cpu-utilization} gives a time series graph to show the
behavior of the same workload, 2 sequencers, with balancing turned on and off.
The curves are the throughputs (\(y\) axis) over time (\(x\) axis) and the graph
has been partitioned into the two cluster setups. The CPU utilization is
confined to one core the MDS is not multithreaded, as it has been shown that
metadata performance does not improve with multiple
threads~\cite{konstantinos:pdsw2014-lustre-metadata}.

@@

\textbf{The Malacology Principle:} Re-uses the Ceph metadata migration, load
balancing, cache coherence, and capabilities subsystems of the MDS. Applying
Mantle's load balancing policy shows 2.02\(\times\) performance improvement and
16\% degradation in performance over the baseline, even though the baseline has
half as many clients.

@@

\begin{figure}[t]
\centering
\includegraphics{figures/recovery-seq-thruput.png}
\caption{The sequencer using Mantle also inherits all the recovery protocols of
the Ceph metadata cluster. The throughput of the sequencer drops when we
terminal MDS 0. The performance quickly resumes and the sequencer is only down
for 15 seconds.}
\label{fig:recovery-seq-thruput}
\end{figure}

This experiment shows how a sequencer handing out tokens can use the Ceph MDS
recovery protocols to recover. For this workload, two sequencers are running on
a metadata cluster {\it without} multiple active MDS nodes. In this cluster,
MDS 1 and MDS 2 are in ``standby" mode, meaning one of them will step in should
the head MDS 0 fail. At the 60 second mark, we manually kill MDS 0.

Figure~\ref{fig:recovery-seq-thruput} shows the sequencer throughput (\(y\)
axis) over time (\(x\) axis). When MDS 0 dies, the MON cluster notices and
quickly assigns a new MDS to handle the namespace. This is when MDS 1 takes
over the sequencer duties and starts handing out tokens.

\textbf{The Malacology Principle:} Re-uses the Ceph metadata protocols for
failure detection and recovery. The sequencer recovers in 15 seconds on a new
MDS and it maintains the same throughput that it had before the failure.
